PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-17 paper/sec-doublecounting.tex
Remove wrong statement

It is interesting
to note that one can tune the QED parton shower to mimic NLO EW effects for specific processes and observables, so that a prediction only accurate at NLO
QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see for example the behaviour of predictions showered with
\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in ref.~\cite{CarloniCalame:2016ouw}). However, this kind of agreement
always comes \emph{a posteriori}, and cannot be ensured in general.
Furthermore, the deconvolution of QED effects in data introduces a dependence on the program (and possibly on 
the specific version) employed for the shower inversion. 
This fact is especially problematic if deconvolved datasets are the only ones which are published, since undoing the exact deconvolution can be very difficult, or practically impossible.
(\textbf{TODO insert comment about LEP ISR and DIS EW effects removal}).

A more physical definition of leptonic observables would be one making use of either bare leptons (the leptons as they emerge after FSR)
or of dressed leptons (leptons and photons are clustered together and their momenta are combined, in analogy with jets in QCD). The problem with the former is that 
electrons are never measured as bare particles, because of the finite resolution 
of the electromagnetic calorimeter. For what concerns muons, while in principle the concept of a bare muon is physical, it should be kept in
mind that modern, general-purpose codes employed to
compute EW corrections treat leptons as massless, to ensure numerical stability of the matrix elements. In this case, using bare leptons is not collinear safe.
Dressed leptons avoid all these shortcomings, with the further advantage of being
inclusive on the effect of extra collinear emissions. This fact encourages to explore the possibility of employing a dressed-lepton
definition, regardless of the leptonic flavour. We acknowledge that this practice is already being followed in (some) experimental analyses:
indeed, to mention two examples discussed in this paper, in ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
and bare ones, while refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition. We therefore recommend that these ways of presenting the experimental
data becomes standard in the future.

>>>>

It is interesting
to note that one can tune the QED parton shower to mimic NLO EW effects for specific processes and observables, so that a prediction only accurate at NLO
QCD displays a remarkable agreement with another at NLO QCD+EW when the photonic shower is included (see also the behaviour of predictions showered with
\textsc{Photos}~\cite{Barberio:1990ms,Barberio:1993qi,Golonka:2005pn} in ref.~\cite{CarloniCalame:2016ouw}).
However, this kind of agreement
always comes \emph{a posteriori}, and cannot be ensured in general.
The transverse momentum of the Z boson as shown in section~\ref{sec:Zpt} is such an example: the difference between the two datasets is rather small (less than \SI{6}{\percent}), but the NLO EW corrections are as large as \SI{25}{\percent}.
Furthermore, the deconvolution of QED effects in data introduces a dependence on the program (and possibly on 
the specific version) employed for the shower inversion. 
This fact is especially problematic if deconvolved datasets are the only ones which are published, since undoing the exact deconvolution can be very difficult, or practically impossible.
(\textbf{TODO insert comment about LEP ISR and DIS EW effects removal}).

A more physical definition of leptonic observables would be one making use of either bare leptons (the leptons as they emerge after FSR)
or of dressed leptons (leptons and photons are clustered together and their momenta are combined, in analogy with jets in QCD). The problem with the former is that 
electrons are never measured as bare particles, because of the finite resolution 
of the electromagnetic calorimeter. For what concerns muons, while in principle the concept of a bare muon is physical, it should be kept in
mind that modern, general-purpose codes employed to
compute EW corrections treat leptons as massless, to ensure numerical stability of the matrix elements. In this case, using bare leptons is not collinear safe.
Dressed leptons avoid all these shortcomings, with the further advantage of being
inclusive on the effect of extra collinear emissions. This fact encourages to explore the possibility of employing a dressed-lepton
definition, regardless of the leptonic flavour. We acknowledge that this practice is already being followed in (some) experimental analyses:
indeed, to mention two examples discussed in this paper, in ref.~\cite{Aad:2015auj} data for dressed leptons are published, together with the Born-level
and bare ones, while refs.~\cite{Sirunyan:2019bzr} employs a dressed-lepton definition. We therefore recommend that these ways of presenting the experimental
data become standard in the future.
